\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Virochaan Ravichandran Gowri & 3\\
Omar Al-Asfar & 3\\
Rayyan Suhail & 3\\
Ibrahim Quraishi & 3\\
Mohammad Mahdi Mahboob & 3\\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

\noindent \textbf{Supervisor's Name: } [Luke Schurmann]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2\\
Virochaan Ravichandran Gowri & 2\\
Omar Al-Asfar & 2\\
Rayyan Suhail & 2\\
Ibrahim Quraishi & 2\\
Mohammad Mahdi Mahboob & 2\\
\bottomrule
\end{tabular}
\end{table}

One supervisor meeting is scheduled for March 26th, 2026. Every team member is expected to join (This document will be updated otherwise).

\section{Lecture Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Virochaan Ravichandran Gowri & 0\\
Omar Al-Asfar & 0\\
Rayyan Suhail & 0\\
Ibrahim Quraishi & 0\\
Mohammad Mahdi Mahboob & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: } [Tiago de Moraes Machado]

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Virochaan Ravichandran Gowri & 1\\
Omar Al-Asfar & 1\\
Rayyan Suhail & 1\\
Ibrahim Quraishi & 1\\
Mohammad Mahdi Mahboob & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 552 & 100\% \\
Virochaan Ravichandran Gowri & 225 & 40\% \\
Omar Al-Asfar & 81 & 15\% \\
Rayyan Suhail & 64 & 12\% \\
Ibrahim Quraishi & 108 & 19\% \\
Mohammad Mahdi Mahboob & 74 & 14\% \\
\bottomrule
\end{tabular}
\end{table}

Explanation from Rev 0 applies here: \\
\textit{While there are visible differences in contribution percentages, there is a similar pattern to the POC Team Contribution report. The differences can be attributed to the same reasoning as before, with members commiting at different frequencies. For instance, Virochaan and Ibrahim tend to commit more frequently than the rest. Omar ranks 3rd in commit count, but contributed the highest in terms of lines of code, with Mohammad following a similar pattern. The line contributions can also be misleading since Virochaan and Omar were responsible for app setup and integration of provided templates, resulting in a higher number of lines than the rest. Rayyan focused more on testing and developed components with less volume, but still essential to the project. Overall, while commit counts vary, all members are comfortable with the workload distribution.}


\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Virochaan Ravichandran Gowri & 59 & 44 \\
Omar Al-Asfar & 23 & 44 \\
Rayyan Suhail & 24 & 45 \\
Ibrahim Quraishi & 27 & 32 \\
Mohammad Mahdi Mahboob & 32 & 42 \\
\bottomrule
\end{tabular}
\end{table}

\section{Team Charter Trigger Items}

The team charter triggers are defined in the Development Plan, aiming to assess team performance. The triggers are as follows:
\begin{itemize}
    \item \textbf{Attendance:} All members are expected to attend meetings punctually for the entire agreed upon duration. Repeated unexcused absences constitue a trigger violation.
    \item \textbf{Communication:} All members are expected to respond to team communications within 24 hours. Failure to respond within this timeframe is considered a trigger violation. Moreover, failure to communicate scheduling difficulties or absences in advance is also considered a communication violation.
    \item \textbf{Quality:} All members are expected to complete their assigned tasks to an agreed upon standard. Repeated and blatant lack of effort or quality in completed tasks is considered a trigger violation. Members are expected to seek help from the team if they are struggling to complete their tasks to the expected standard. Failure to do so reflects on the entire team and is therefore a quality violation.
    \item \textbf{Attitude:} All members are expected to maintain a respectful and open-minded attitude towards each other. A good attitude facilitates effective teamwork and communication. Repeated negative or disrespectful behaviour is considered a trigger violation. Differences of opinion and conflict are not excusable under this trigger. All members are expected to address any issues maturely and professionally based on the team charter guidelines.
    \item \textbf{Contribution:} All members are expected to contribute equitably to the workload. Members are expected to proactively seek out tasks and responsibilities to support the team. Failure to achieve agreed upon performance metrics is a trigger violation. These expectations differ depending on the task, and may include number of commits, software features, lines of code, or even idea generation. The team will agree upon these metrics and expectations at the start of each phase.
\end{itemize}
All members agree that expectations have been met and no trigger violations have occurred thus far. We regularly communicate to ensure universal satisfaction with workload distribution, task quality, and the general direction of the project. Overall, the team is functioning well and there are no concerns regarding team performance at this time.

\section{Additional Productivity Metrics}

The additional productivity metrics we considered previously were pull requests (by involvment i.e. author, assignee, reviewer). The pull request contributions for the entire term are as follows: 

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Pull Requests} & \textbf{Percent}\\
\midrule
Total & 127 & 100\% \\
Ibrahim Quraishi & 16 & 13\% \\
Virochaan Ravichandran Gowri & 45 & 35\% \\
Rayyan Suhail & 23 & 18\% \\
Mohammad Mahdi Mahboob & 25 & 20\% \\
Omar Al-Asfar & 18 & 14\% \\
\bottomrule
\end{tabular}
\end{table}

This table shows a much more accurate estimation of the contributions made. Virochaan has a higher number of pull requests due to the creation of self-assigned and self-reviewed pull requests due to merging between the dev and prod branches.

\end{document}