% THIS DOCUMENT IS FOLLOWS THE VOLERE TEMPLATE BY Suzanne Robertson and James Robertson
% ONLY THE SECTION HEADINGS ARE PROVIDED
%
% Initial draft from https://github.com/Dieblich/volere
%
% Risks are removed because they are covered by the Hazard Analysis
\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{enumerate}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
      colorlinks=true,      % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\newcommand{\lips}{\textit{Insert your content here.}}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Software Requirements Specification for \progname: subtitle describing software} 
\author{\authname}
\date{\today}
	
\maketitle

~\newpage

\pagenumbering{roman}

\tableofcontents

~\newpage

\subsection*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\textbf{Date}} & {\textbf{Version}} & {\textbf{Notes}}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage
\section{Project Drivers}
\subsection{Purpose of the Project}
\subsubsection{User Business}
\lips
\subsubsection{Goals of the Project}
\lips
\subsection{Stakeholders}
\subsubsection{Client}
The client for this project is the supervisor, Luke Schuurman. He is a member of the MES and has first hand experience plannig and hosting events with the MES. As the supervisor he will play a crucial role by ensuring the project aligns with objective of the MES and integrate the platform seamlessly with existing systems. He will also provide us with feedback and guidance throughout the project and will help define the project requirements in this document.
\subsubsection{Customer}
Refer to client
\subsubsection{Other Stakeholders}
Irrelevant
\subsubsection{Hands-On Users of the Project}
\textbf{MES Executives and Council Members}: They will be utilizing this system to create and manage events, configure forms and surveys, monitor event data and generate data analytics reports. They can be characterized as primarily undergraduate students who value their time greatly. They aim to reduce the time taken to do administrative tasks as well as provide a better experience during MES events. Their experience with systems like this can range from Journeyman - Master as they can be experienced in event planning and student engagement. There may be a slight learning curve to utilizing the new technology but these users have experience performing these functions.\\
\newline
\textbf{McMaster Engineering Students}: They will be utilizing this app to to register for events, purchase tickets, sign waivers, check in at venues, and complete feedback surveys. They want to enjoy their university experience and connect with other students, They are also very busy and value their time greatly so are looking for an intuitive and straightforward user experience. Their general experience with systems like this is Journeyman as they may have used similar systems for other use cases. \\
\newline
\textbf{Other Students and Guest Event Attendees}: This group includes non-engineering students, alumni, and invited guests who participate in large-scale MES events such as the Fireball Formal and Graduation Formal, which extend beyond the core engineering community. It could also include students and guests from other universities as well as industry which attend the engineering conferences that the MES helps host. They are generally looking for an easy and seamless experience registering and attending these events. Their general experience with systems like this is Journeyman as they may have used similar systems for other use cases.
\subsubsection{Personas}
\begin{enumerate}
  \item \textbf{Matthew Cruise (Engineering Student)}: Matthew is a 20-year-old second-year Mechanical Engineering student at McMaster University.Hewho lives in a shared house near campus with two close friends. He enjoys attending MES events like pub nights and the Fireball Formal as a way to balance his heavy academic workload with some enjoyment and entertainment. He usually hears about events through word-of-mouth or social media and would prefer an easy and effortless way to find and register for events. Matthew is generally tech savvy and is comfortable using online platforms but doesn't want to be bothered by too many notifications and forms. He has many ideas on how he can generally improve his university experience but doesn't believe he has an outlet to convey them. For Matthew his priority is convenience as he wants to enjoy himself but doesn't want to spend too much time or effort doing so.
  \item \textbf{Adam Clooney (MES Executive)}: Adam Clooney is a 22-year-old final-year Civil Engineering student who currently serves as VP Social on the MES. He is responsible for coordinating large-scale events like Fireball Formal, working closely with other council members to handle logistics, advertising, and student engagement. Adam is outgoing and enjoys bringing people together, but often feels the strain of balancing his role with academic responsibilities. He is proficient with common digital tools such as Google Drive, spreadsheets, and design platforms for promotions, but he’s not highly technical. Adam appreciates structure and tools that keep things organized because he dislikes wasting time fixing errors or repeating work. He is motivated by the sense of accomplishment that comes from hosting a successful event and wants tools that help him stay on top of details.
  \item \textbf{Margot Watson (McMaster Student)}: Margot Watson is a 21-year-old undergraduate student in Political Science at McMaster University. Although she is not part of the engineering faculty, she often attends large MES-hosted events such as the Fireball Formal and other socials because many of her friends are in engineering. Margot lives in an off-campus apartment with two roommates and enjoys being involved in student life across faculties. She has a relaxed attitude toward technology since she uses her phone daily for social media and messaging but she prefers things to be straightforward and intuitive. She is cautious with her money, balancing tuition and living expenses, but she’s willing to spend on experiences with friends. She is motivated by spending time with her friends and having good experiences to have a fullfiling student life.
\end{enumerate}
\subsubsection{Priorities Assigned to Users}
\textbf{Key Users:} Luke Schuurman, MES Council Members and Executives, McMaster Engineering Students. \\
\textbf{Secondary Users:} Other Students and Guest Event Attendees.
\subsubsection{User Participation}
Our requirements will primarily be derived through meetings with our supervisor Luke Schuurman. If we have the need to clarify or elicit more requirements we will look to engage other MES members either through our supervisor or directly.
\subsubsection{Maintenance Users and Service Technicians}
\textit{The future maintenance and servicing of this project are beyond the scope of this capstone.}
\section{Project Constraints}
\subsection{Mandated Constraints}
\subsubsection{Solution Constraints}
\lips
\subsubsection{Implementation Environment of the Current System}
\lips
\subsubsection{Partner or Collaborative Applications}
\lips
\subsubsection{Off-the-Shelf Software}
\lips
\subsubsection{Anticipated Workplace Environment}
\lips
\subsubsection{Schedule Constraints}
\lips
\subsubsection{Budget Constraints}
\lips
\subsubsection{Enterprise Constraints}
\lips

\subsection{Naming Conventions and Terminology}
\begin{itemize}
  \item \textbf{MES}: McMaster Engineering Society
\end{itemize}
\subsubsection{Glossary of All Terms, Including Acronyms, Used by Stakeholders
involved in the Project}
\lips

\subsection{Relevant Facts And Assumptions}
\subsubsection{Relevant Facts}
\lips
\subsubsection{Business Rules}
\lips
\subsubsection{Assumptions}
\lips

\section{Functional Requirements}
\subsection{The Scope of the Work}
\subsubsection{The Current Situation}
\lips
\subsubsection{The Context of the Work}
\lips
\subsubsection{Work Partitioning}
\lips
\subsubsection{Specifying a Business Use Case (BUC)}
\lips

\subsection{Business Data Model and Data Dictionary}
\subsubsection{Business Data Model}
\lips
\subsubsection{Data Dictionary}
\lips

\subsection{The Scope of the Product}
\subsubsection{Product Boundary}
\lips
\subsubsection{Product Use Case Table}
\lips
\subsubsection{Individual Product Use Cases (PUC's)}
\lips

\subsection{Functional Requirements}
\subsubsection{Functional Requirements}
\lips

\section{Non-Functional Requirements}
\subsection{Look and Feel Requirements}
\subsubsection{Appearance Requirements}
\lips
\subsubsection{Style Requirements}
\lips

\subsection{Usability and Humanity Requirements}
\subsubsection{Ease of Use Requirements}
\lips
\subsubsection{Personalization and Internationalization Requirements}
\lips
\subsubsection{Learning Requirements}
\lips
\subsubsection{Understandability and Politeness Requirements}
\lips
\subsubsection{Accessibility Requirements}
\lips

\subsection{Performance Requirements}
\subsubsection{Speed and Latency Requirements}
\lips
\subsubsection{Safety-Critical Requirements}
\lips
\subsubsection{Precision or Accuracy Requirements}
\lips
\subsubsection{Robustness or Fault-Tolerance Requirements}
\lips
\subsubsection{Capacity Requirements}
\lips
\subsubsection{Scalability or Extensibility Requirements}
\lips
\subsubsection{Longevity Requirements}
\lips

\subsection{Operational and Environmental Requirements}
\subsubsection{Expected Physical Environment}
\lips
\subsubsection{Wider Environment Requirements}
\lips
\subsubsection{Requirements for Interfacing with Adjacent Systems}
\lips
\subsubsection{Productization Requirements}
\lips
\subsubsection{Release Requirements}
\lips

\subsection{Maintainability and Support Requirements}
\subsubsection{Maintenance Requirements}
\begin{enumerate}[{MSR}1.] 
  \item \label{MSR1} 
  \begin{itemize}
    \item Rationale:
    \item Fit Criterion:
  \end{itemize}
\end{enumerate}
\subsubsection{Supportability Requirements}
\lips
\subsubsection{Adaptability Requirements}
\lips

\subsection{Security Requirements}
\subsubsection{Access Requirements}
\lips
\subsubsection{Integrity Requirements}
\lips
\subsubsection{Privacy Requirements}
\lips
\subsubsection{Audit Requirements}
\lips
\subsubsection{Immunity Requirements}
\lips

\subsection{Cultural Requirements}
\subsubsection{Cultural Requirements}
\lips

\subsection{Compliance Requirements}
\subsubsection{Legal Requirements}
\lips
\subsubsection{Standards Compliance Requirements}
\lips

\section{Project Issues}
\subsection{Open Issues}
\lips

\subsection{Off-the-Shelf Solutions}
\subsubsection{Ready-Made Products}
There are some products that exists on the market which solve certain components of this product but no product exists that combines these components into one. For event management there are various tools such as EventBrite and Stubhub which can allow for the selling of tickets for events. The problem with these products are that they don't integrate well with current MES Systems and don't provide all the features as required such as collecting waivers and ensuring McMaster students attend university specific events. For general data collection Google Forms is the most used tool and it allows for the creation of complex forms and stores data in spreadsheets. For further data analysis it requires effort on the part of the form creator to actually go and analyze the data to gain actual insights. Also the forms can become hard to handle as they become complex and can become confusing for respondents. As mentioned before there is no tool that has a combination of the two components.
\subsubsection{Reusable Components}
There are various components that we can use to help develop our application:
\begin{itemize}
  \item \textbf{Next.JS}: Provide us with a framework for developing web apps in \textbf{React} and provides built in routing behaviour. It also handles many built in libraries and packages that we can use for front-end styling such as \textbf{tailwind-css} and \textbf{shadcn/ui}. We can also integrate it with other libraries for authentication and for database management
  \item \textbf{SurveyJS}: This is a potential tool we can use to develop the form builder as it provides us with some pre-built components we can use to develop and customize our own forms. 
  \item \textbf{Recharts}: This could be potential charting tool we can use to develop our admin dashboard. Though there are other charting tools the benefit of Recharts is that it provides customization on top of the pre built charts.
  \item \textbf{Drizzle}: We can use Drizzle as an ORM to map from our database to our web-app. Drizzle is useful since it is lightweight and is code first. Drizzle's simplicity allows for faster development and is perfect for our use case.
\end{itemize}
These components will allow us to develop our application faster and more efficiently as many of these products are already optimized. All the above products are free to use so do not incur any extra costs or require the handling of licenses.
\subsubsection{Products That Can Be Copied}
\textit{There don't seem to be any products that can be copied which contain all the required components within a single product. Moreover the MES wants a product that doesn't require an external license and wants to be fully built in house so they have control over future development and usage.}

\subsection{New Problems}
\subsubsection{Effects on the Current Environment}
\lips
\subsubsection{Effects on the Installed Systems}
\lips
\subsubsection{Potential User Problems}
\lips
\subsubsection{Limitations in the Anticipated Implementation Environment That May
Inhibit the New Product}
\lips
\subsubsection{Follow-Up Problems}
\lips

\subsection{Tasks}
\subsubsection{Project Planning}
\lips
\subsubsection{Planning of the Development Phases}
\lips

\subsection{Migration to the New Product}
\subsubsection{Requirements for Migration to the New Product}
\lips
\subsubsection{Data That Has to be Modified or Translated for the New System}
\lips

\subsection{Costs}
We don't expect any costs to arise during the development of the project. We will be using free tools and libraries for development and for hosting we will look to host databases and the back-end locally. In production the hosting will be done by the MES so it is out of the scope of this capstone.
\subsection{User Documentation and Training}
\subsubsection{User Documentation Requirements}
\lips
\subsubsection{Training Requirements}
\lips

\subsection{Waiting Room}
\lips

\subsection{Ideas for Solution}
\lips

\newpage{}
\subsection*{Appendix --- Reflection}

\input{../Reflection.tex}

\input{../SRS_Reflection.tex}

\end{document}