\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Reflection and Traceability Report on \progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\section{Changes in Response to Feedback}

\plt{Summarize the changes made over the course of the project in response to
feedback from TAs, the instructor, teammates, other teams, the project
supervisor (if present), and from user testers.}

\plt{For those teams with an external supervisor, please highlight how the feedback 
from the supervisor shaped your project.  In particular, you should highlight the 
supervisor's response to your Rev 0 demonstration to them.}

\plt{Version control can make the summary relatively easy, if you used issues
and meaningful commits.  If you feedback is in an issue, and you responded in
the issue tracker, you can point to the issue as part of explaining your
changes.  If addressing the issue required changes to code or documentation, you
can point to the specific commit that made the changes.  Although the links are
helpful for the details, you should include a label for each item of feedback so
that the reader has an idea of what each item is about without the need to click
on everything to find out.}

\plt{If you were not organized with your commits, traceability between feedback
and commits will not be feasible to capture after the fact.  You will instead
need to spend time writing down a summary of the changes made in response to
each item of feedback.}

\plt{You should address EVERY item of feedback.  A table or itemized list is
recommended.  You should record every item of feedback, along with the source of
that feedback and the change you made in response to that feedback.  The
response can be a change to your documentation, code, or development process.
The response can also be the reason why no changes were made in response to the
feedback.  To make this information manageable, you will record the feedback and
response separately for each deliverable in the sections that follow.}

\plt{If the feedback is general or incomplete, the TA (or instructor) will not
be able to grade your response to feedback.  In that case your grade on this
document, and likely the Revision 1 versions of the other documents will be
low.} 

\subsection{SRS and Hazard Analysis}

\subsection{Design and Design Documentation}

\subsection{VnV Plan and Report}

\section{Extras}

\plt{Summarize the extras that were tackled by this project.  Extras
can include usability testing, code walkthroughs, user documentation, formal
proof, GenderMag personas, Design Thinking, etc.  Extras should have already
been approved by the course instructor as included in your problem statement.}

\section{Design Iteration}

Our front-end design underwent revisions based on supervisor feedback, who
evaluated the product as an end-user for both attendee and admin portals as
part of our usability testing. The UI for specified sections was revamped to
address the concerns raised.

The underlying architecture remained the same as the client was clear and
specific about how the system should interact with the environment and how
data should be stored. As a result, it was possible to satisfy requirements
with the initial architecture.

\subsection{Usability Testing}

Usability testing directly influenced our UI design,

\subsubsection{User Profile Configuration}

\begin{itemize}
    \item \textbf{Problem:} Manual re-entry of user details for every event is
    redundant for participants and creates administrative overhead when
    designing registration forms.
    \item \textbf{Solution:} Implement a mandatory user profile system that
    automatically populates relevant fields in registration tables, streamlining
    the enrollment process.
\end{itemize}

\subsubsection{Form Builder Survey Creation Automation}

\begin{itemize}
    \item \textbf{Problem:} Manual form construction is labor-intensive and
    error-prone, particularly when managing large-scale surveys.
    \item \textbf{Solution:} Support CSV template uploads to automate form
    generation, significantly reducing development time and ensuring data
    consistency.
\end{itemize}

\subsubsection{UI Consistency}
\begin{itemize}
    \item \textbf{Problem:} Fragmented UI Components and Aesthetic Inconsistency
    \begin{itemize}
        \item Disparity between custom UI library components and native
        browser-default form elements (e.g., buttons, inputs, and dropdowns).
        \item Non-uniform colour application and lack of a cohesive visual
        identity across different modules.
    \end{itemize}
    
    \item \textbf{Rationale:} Enhanced Platform Literacy and User Intuition
    \begin{itemize}
        \item A standardized interface reduces cognitive load, allowing users to
        predict behavior based on established visual patterns.
        \item Consistent design strengthens brand identity and provides a more
        professional, polished user experience.
    \end{itemize}
    
    \item \textbf{Solution:} Global Component Standardization
    \begin{itemize}
        \item Refactor all modals and interactive elements to strictly utilize
        the primary UI library.
        \item Enforce a unified design system for state-dependent styling,
        specifically for:
        \begin{itemize}
            \item High-contrast borders for selected or focused elements.
            \item Standardized hover states and active press feedback.
            \item Consistent padding, shadows, and corner radii across all containers.
        \end{itemize}
    \end{itemize}
\end{itemize}

\begin{itemize}
    \item \textbf{Problem:} Lack of Visual Feedback for Multi-Step Workflows
    \begin{itemize}
        \item Users have no clear indication of completion status when
        navigating modular surveys or multi-page forms.
        \item Absence of "save-and-continue" context leads to uncertainty and
        higher abandonment rates.
    \end{itemize}
    
    \item \textbf{Rationale:} Cognitive Mapping and Completion Motivation
    \begin{itemize}
        \item Visualizing progress provides a "mental map" of the task, reducing
        the perceived effort of long forms.
        \item Constant feedback reinforces a sense of accomplishment,
        encouraging users to finish the registration or survey.
    \end{itemize}
    
    \item \textbf{Solution:} Integrated Progress Tracking System
    \begin{itemize}
        \item Implement a dynamic progress bar or "stepper" component at the top
        of modular interfaces.
        \item Enhance the UI with specific status indicators, including:
        \begin{itemize}
            \item \textbf{Percentage Completion:} A real-time calculation of
            answered versus total required fields.
            \item \textbf{Sectional Checkmarks:} Visual confirmation when an
            entire module or category is successfully validated.
            \item \textbf{Time-to-Complete Estimates:} Providing an approximate
            remaining duration based on average user interaction.
        \end{itemize}
    \end{itemize}
\end{itemize}

\section{Design Decisions}

 \subsection{Limitations}
There were no identifiable limitations. All design decisions were based on
assumptions and constraints.

 \subsection{Assumptions}
Certain assumptions about event-day proceedings have influenced how we track and
show attendance statuses for event participants. In the current system, it is
assumed that once attendees have checked-in at the event, they are given a
physical indicator of their attendance on-site, such as a wristband or a stamp.
As a result, there is no software indicator in the attendee portal which can be
used to demonstrate to event administrators that the user has checked-in to the
event. This is a decision we are happy to make as it reduces the workload
required for an MVP, and there is a system in place already which does not need
to be replaced which addresses this issue.

\subsection{Constraints}
\subsubsection{Technological Constraints}
The technological constraints determined by our client influenced our design,
especially our backend and data architecture. The tech stack constraints
required us to use JavaScript and TypeScript-based backend frameworks and
methodologies to implement our APIs and routing. Our data needed to be formatted
and stored in a relational database as we used a SQL DBMS. These constraints
also required us to deploy using our client's hosted server as it was compatible
with the deployment technology used for our backend. As a result of using JS and
TS-based frameworks, error handling and complete case coverage was less prioritized
where possible in order to deliver an MVP faster.

The requirement to implement a bespoke form builder and form submission system
meant we could not use any pre-existing open-source form libraries. This
required us to design how modular forms interact with each other, how they
stored with respect to the relational database, and how they are rendered to the
user. We decided to implement modular surveys as a series of independent
surveys, with sections unlocking if necessary based on specific responses or the
completion of previous sections. This ensured our form builder was meaningfully
different from existing form-building software, and provides the client with the
flexibility to reuse form results and make surveys digestible for attendees when
they complete them.

\subsubsection{Scheduling Constraints}
The initial and revised scheduling constraints influenced our MVP features. We
decided to forego a fully-integrated login system with the McMaster ecosystem as
specific features such as the ability to purchase multiple tickets or transfer
tickets to other users. We recognized that these changes are trivial compared to
the features we have deployed in our MVP, so pushing it in the backlog made sense
from a continuous and iterative development process perspective.

\subsubsection{Expandability \& Integration Constraints}
One of the stretch goals of this project was to provide this product as a SAAS
product for organizations outside of the McMaster Engineering Society to use.
The initial plan of the software was also to be integrated with software from
other groups within the same ecosystem, though this later changed. As a result,
our API and database design remained mostly detatched from McMaster-specific
infrastructure, making it more portable. This design decision helped with
abstraction of the system, and made front-end integration simpler as API routes
were well-defined.

\section{Economic Considerations (LO23)}

\plt{Is there a market for your product? What would be involved in marketing your 
product? What is your estimate of the cost to produce a version that you could 
sell?  What would you charge for your product?  How many units would you have to 
sell to make money? If your product isn't something that would be sold, like an 
open source project, how would you go about attracting users?  How many potential 
users currently exist?}

\section{Reflection on Project Management (LO24)}

\plt{This question focuses on processes and tools used for project management.}

\subsection{How Does Your Project Management Compare to Your Development Plan}

\plt{Did you follow your Development plan, with respect to the team meeting plan, 
team communication plan, team member roles and workflow plan.  Did you use the 
technology you planned on using?}

\subsection{What Went Well?}

\plt{What went well for your project management in terms of processes and 
technology?}

\subsection{What Went Wrong?}

\plt{What went wrong in terms of processes and technology?}

\subsection{What Would you Do Differently Next Time?}

\plt{What will you do differently for your next project?}

\section{Ethics and Equity (LO18)}

\plt{Describe how your team applied the principle of equity and universal design
to ensure equitable treatment of all stakeholders.}

\section{Reflection on Capstone}

\plt{This question focuses on what you learned during the course of the capstone project.}

\subsection{Which Courses Were Relevant}

\plt{Which of the courses you have taken were relevant for the capstone project?}

\subsection{Knowledge/Skills Outside of Courses}

\plt{What skills/knowledge did you need to acquire for your capstone project
that was outside of the courses you took?}

\end{document}