\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{longtable}
\usepackage[table]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date 1 & 1.0 & Notes\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  \bottomrule
\end{tabular}\\

\wss{symbols, abbreviations or acronyms -- you can reference the SRS tables if needed}

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document ...

\section{Functional Requirements Evaluation}
\subsection{Area of Testing 1: Admin Portal}
\subsubsection{Test-FR-AP-1: Create Form}
\textbf{Type:} Manual \\ \textbf{Initial State:} Administrator is logged into the admin portal with permission to create forms. \\ \textbf{Test Procedure:}
\begin{verbatim}
Input:
- Navigate to the form creation page
- Enter form name = "Event Feedback Form"
- Add field: Text field labelled "Name"
- Add field: Checkbox labelled "Events Attended"
- Add field: Rating field labelled "Overall Experience"
- Click "Create Form"
\end{verbatim}
\textbf{Expected Result:}
\begin{verbatim}
Output:
- System confirms successful form creation
- Newly created form appears in the admin dashboard
- Form fields are stored correctly in the database
\end{verbatim}
\textbf{Result:} Pass \\ 
\textbf{Discussion:} The administrator successfully created a new form with multiple fields and the form appeared correctly in the dashboard with all fields stored in the system database. \\
\subsubsection{Test-FR-AP-2: View and Analyze Form Data}
\textbf{Type:} Manual \\ \textbf{Initial State:} At least two forms exist with previously collected responses. \\ \textbf{Test Procedure:}
\begin{verbatim}
Input:
- Navigate to the analytics dashboard
- Select multiple forms with collected responses
- Click "View Analytics"
\end{verbatim}
\textbf{Expected Result:}
\begin{verbatim}
Output:
- Aggregated analytics are displayed
- Charts and response summaries appear
- Displayed analytics match stored backend data
\end{verbatim}
\textbf{Result:} Pass \\ \textbf{Discussion:} The analytics dashboard correctly aggregated the responses from multiple forms and displayed charts and summary statistics consistent with the stored backend data. \\
\subsubsection{Test-FR-AP-3: Manage Events via Dashboard}
\textbf{Type:} Manual \\ \textbf{Initial State:} Multiple events exist in the system with various payment statuses. \\ \textbf{Test Procedure:}
\begin{verbatim}
Input:
- Navigate to the admin dashboard
- Select the filter option
- Apply filter "Pending Payment"
\end{verbatim}
\textbf{Expected Result:}
\begin{verbatim}
Output:
- Dashboard displays only events with pending payment status
- Displayed events match stored system records
\end{verbatim}
\textbf{Result:} Pass \\ \textbf{Discussion:} The dashboard filtering functionality worked correctly and displayed only the events matching the selected payment status filter. \\
\subsubsection{Test-FR-AP-4: View and Export Event Analytics}
\textbf{Type:} Manual \\ \textbf{Initial State:} Events exist with collected survey responses. \\ \textbf{Test Procedure:}
\begin{verbatim}
Input:
- Navigate to the event analytics dashboard
- Select an event with stored responses
- Click "Export Analytics"
\end{verbatim}
\textbf{Expected Result:}
\begin{verbatim}
Output:
- Event analytics are displayed in the dashboard
- System generates a downloadable report file
- Exported data matches the analytics displayed
\end{verbatim}
\textbf{Result:} Pass \\ \textbf{Discussion:} The export functionality successfully generated a downloadable analytics report containing the correct event statistics and survey response summaries. \\
\subsection{Area of Testing 2: Attendee Application}
This section evaluates the functional requirements specific to the attendee's mobile experience. Testing focuses on the end-to-end journey for students, including registration workflows, event discovery, and the feedback submission process.

\subsubsection{Test-FR-AA-1: Register for Event}
\textbf{Type:} Automatic \\
\textbf{Initial State:} An event is open and attendee is authenticated. \\
\textbf{Input/Condition:} Attendee submits an event registration form. \\
\textbf{Expected Output:} Registration is saved and a confirmation message is displayed and sent to attendee and a QR ticket is generated. \\
\textbf{How the test will be performed:} An automated test script will simulate a form submission for a test event and verify the existence of the generated QR code object in the database and the success response from the server. \\
\textbf{Actual Result:} The registration was processed successfully; a unique QR ticket was generated and linked to the attendee's profile in the database.

\subsubsection{Test-FR-AA-2: Access Event Listings}
\textbf{Type:} Manual \\
\textbf{Initial State:} The system has multiple upcoming and past events. \\
\textbf{Test Procedure:} \\
\textbf{Input:} 
\begin{itemize}
    \item Login as an authenticated attendee.
    \item Navigate to the "Upcoming Events" tab.
    \item Navigate to the "Registered Events" tab.
    \item Select a specific event to view its details.
\end{itemize}
\textbf{Expected Result:} \\
\textbf{Output:} 
\begin{itemize}
    \item Each tab displays the correct filtered list of events.
    \item Event information (time, location, description) accurately matches the database records.
\end{itemize}
\textbf{Result:} Pass \\
\textbf{Discussion:} The attendee was able to browse all available events and view their specific registered events without discrepancy between the UI and the backend data.

\subsubsection{Test-FR-AA-3: Fill out Form}
\textbf{Type:} Automatic \\
\textbf{Initial State:} A survey is available and attendee is authenticated. \\
\textbf{Input/Condition:} Attendee completes and submits the survey. \\
\textbf{Expected Output:} Survey responses are stored and a confirmation message appears. \\
\textbf{How the test will be performed:} Using a headless browser, the system will fill out all required fields in a dynamic feedback form and click submit, then check for a 201 Created status from the API. \\
\textbf{Actual Result:} Feedback data was successfully committed to the database and associated with the correct Event ID.

\subsection{Area of Testing 3: System Integration and Security}
This section verifies the robustness of the system's internal communications and its defensive posture. Testing includes real-time data synchronization between the admin and attendee interfaces, as well as manual verification of role-based access controls to prevent unauthorized data access.

\subsubsection{Test-FR-SI-1: Real-Time Data Synchronization}
\textbf{Type:} Automatic \\
\textbf{Initial State:} Admin and attendee interfaces are active. \\
\textbf{Input/Condition:} Admin updates event details (e.g., venue or date). \\
\textbf{Expected Output:} Attendee view updates automatically without manual refresh. \\
\textbf{How the test will be performed:} A script will trigger a PATCH request to the event endpoint and then verify if the WebSocket listener on the client-side received the payload and updated the local state. \\
\textbf{Actual Result:} The attendee UI updated within 200ms of the admin change, reflecting the new location details without a page reload.

\subsubsection{Test-FR-SI-2: Role-Based Access Verification}
\textbf{Type:} Manual \\
\textbf{Initial State:} Admin and attendee accounts exist with distinct permissions. \\
\textbf{Test Procedure:} \\
\textbf{Input:} 
\begin{itemize}
    \item Login with an "Attendee" role account.
    \item Attempt to access the Admin Dashboard URL manually.
    \item Attempt to trigger a "Create Form" API request using the attendee token.
\end{itemize}
\textbf{Expected Result:} \\
\textbf{Output:} 
\begin{itemize}
    \item The system denies access to admin features.
    \item Proper error handling (e.g., 403 Forbidden or redirection) is observed.
\end{itemize}
\textbf{Result:} Pass \\
\textbf{Discussion:} The system successfully enforced role-based access control, ensuring that sensitive administrative functions are strictly limited to authorized accounts.

\subsubsection{Test-FR-SI-3: API Security - SQL Injection}
\textbf{Type:} Automatic \\
\textbf{Initial State:} System API is live and accepting search queries. \\
\textbf{Input/Condition:} Submit a string containing SQL commands (e.g., "OR 1=1") into the event search bar. \\
\textbf{Expected Output:} The system treats the input as a string and returns no results; no data leak occurs. \\
\textbf{How the test will be performed:} An automated security suite will run a payload of common SQL injection strings against all search endpoints to check for database error leaks or unauthorized data retrieval. \\
\textbf{Actual Result:} All payloads were successfully sanitized or rejected; the database remained secure.

\section{Nonfunctional Requirements Evaluation}

\subsection{System Testing - Look and Feel}
This section evaluates the visual and aesthetic requirements of the EvENGage system, ensuring the user interface aligns with the McMaster Engineering Society's branding and meets stakeholder expectations for professional design.

\subsubsection{Test-NFR-LF-1: MES Branding Conformance}
\textbf{Type:} Manual \\
\textbf{Initial State:} The UI for the basic system build is finalized and accessible. \\
\textbf{Test Procedure:} \\
\textbf{Input:} 
\begin{itemize}
    \item Provide the MES representative with access to the application UI.
    \item Review the color palette, typography, and logo placement against MES branding guidelines.
\end{itemize}
\textbf{Expected Result:} \\
\textbf{Output:} 
\begin{itemize}
    \item Official approval from the MES representative on branding consistency.
\end{itemize}
\textbf{Result:} Pass \\
\textbf{Discussion:} A meeting was held with the stakeholder where the design decisions (branding and color palette) were assessed. The representative confirmed the UI correctly reflects the MES identity.

\subsubsection{Test-NFR-LF-2: Design Reception Survey}
\textbf{Type:} Manual \\
\textbf{Initial State:} A production build has been used in a live event and a survey is ready for distribution. \\
\textbf{Test Procedure:} \\
\textbf{Input:} 
\begin{itemize}
    \item Deploy the app at one MES event.
    \item Send a design reception survey to all attendees.
\end{itemize}
\textbf{Expected Result:} \\
\textbf{Output:} 
\begin{itemize}
    \item Survey results indicating positive user reception of the visual design.
\end{itemize}
\textbf{Result:} Pass \\
\textbf{Discussion:} Survey results were compiled and analyzed. The feedback illustrated that the design meets usability and aesthetic expectations for the target student demographic.

\subsection{System Testing - Usability and Humanity}
This section focuses on the ease of use, accessibility, and user-centric design of the platform for both administrators and student attendees.

\subsubsection{Test-NFR-UH-1: Intuitive Feedback and Registration}
\textbf{Type:} Manual \\
\textbf{Initial State:} Functional live event forms are deployed. \\
\textbf{Test Procedure:} \\
\textbf{Input:} 
\begin{itemize}
    \item Observe 30 attendees accessing the app during an event with no prior instruction.
\end{itemize}
\textbf{Expected Result:} \\
\textbf{Output:} 
\begin{itemize}
    \item Successful submission of registration and feedback forms.
    \item Average ease-of-use rating of 4+ out of 5 from at least 80\% of users.
\end{itemize}
\textbf{Result:} Pass \\
\textbf{Discussion:} Attendees were able to register and provide feedback without any technical guidance, satisfying the requirement for intuitive navigation.

\subsubsection{Test-NFR-UH-6: Accessibility Conformance}
\textbf{Type:} Automatic \\
\textbf{Initial State:} Fully configured UI themes are live. \\
\textbf{Input/Condition:} Web accessibility evaluation tools (e.g., WebAIM) are used to scan the interface. \\
\textbf{Expected Output:} The design conforms to WCAG 2.0 and AODA requirements. \\
\textbf{How the test will be performed:} Automated web tools will be used to assess the DOM structure, color contrast ratios, and screen-reader compatibility. \\
\textbf{Actual Result:} The system successfully passed WCAG 2.0 Level AA compliance checks with no high-priority accessibility errors detected.

\subsection{System Testing - Performance}
This section evaluates the system's responsiveness and capacity, ensuring it can handle the high traffic characteristic of large-scale university events.

\subsubsection{Test-NFR-PF-1: Form Latency}
\textbf{Type:} Automatic \\
\textbf{Initial State:} Platform is open on a variety of devices (iOS, Android, Windows). \\
\textbf{Input/Condition:} Loading event forms. \\
\textbf{Expected Output:} Measured Time to First Byte (TTFB) is less than 2 seconds. \\
\textbf{How the test will be performed:} Browser developer tools and APM monitoring will be used on distinct devices to measure total load time. \\
\textbf{Actual Result:} Average TTFB across all devices was 1.1 seconds, well within the 2-second threshold.

\subsection{System Testing - Security}
This section validates the protection of user data and the integrity of administrative actions within the system.

\subsubsection{Test-NFR-ST-1: Secure Email Authentication}
\textbf{Type:} Manual \\
\textbf{Initial State:} Authentication is configured to restrict access to McMaster email domains. \\
\textbf{Test Procedure:} \\
\textbf{Input:} 
\begin{itemize}
    \item Attempt login with a non-McMaster email address.
    \item Attempt login with a valid @mcmaster.ca email address.
\end{itemize}
\textbf{Expected Result:} \\
\textbf{Output:} 
\begin{itemize}
    \item System denies access to the non-McMaster account and logs the attempt.
    \item System allows access to the valid McMaster account.
\end{itemize}
\textbf{Result:} Pass \\
\textbf{Discussion:} The authentication layer correctly filtered users by domain and provided an audit trail for invalid login attempts.

\subsubsection{Test-NFR-ST-4: Secure Data Encryption}
\textbf{Type:} Manual \\
\textbf{Initial State:} No test account created in the database. \\
\textbf{Test Procedure:} \\
\textbf{Input:} 
\begin{itemize}
    \item Create a new account and submit personal information.
    \item Inspect the database entry for that specific user.
\end{itemize}
\textbf{Expected Result:} \\
\textbf{Output:} 
\begin{itemize}
    \item Personal data fields are fully encrypted with no plaintext visible.
\end{itemize}
\textbf{Result:} Pass \\
\textbf{Discussion:} Direct inspection of the PostgreSQL database confirmed that sensitive data is stored using AES-256 encryption.

\subsection{etc.}
	
\section{Comparison to Existing Implementation}	

This section will not be appropriate for every project.

\section{Unit Testing}

\subsection{Server API Testing}

\subsubsection{Admin Server Testing - Events API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{5cm}|>{\raggedright\arraybackslash}p{3.25cm}|>{\raggedright\arraybackslash}p{3.25cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC1 & GET /api/events - Return all events sorted by date & Events array returned, sorted with future events first & Events returned in correct order & \cellcolor{green!30}Pass \\
\hline
TC2 & GET /api/events - Sort future events before past events & Future events appear before past events in response & Events correctly sorted by date & \cellcolor{green!30}Pass \\
\hline
TC3 & GET /api/events - Handle database errors gracefully & Error response with 500 status code & Error caught and returned & \cellcolor{green!30}Pass \\
\hline
TC4 & POST /api/event/create - Create new event with all required fields & 201 status code with created event data & Event successfully created & \cellcolor{green!30}Pass \\
\hline
TC5 & POST /api/event/create - Create event with default registration form & Default form fields populated & Registration form created with defaults & \cellcolor{green!30}Pass \\
\hline
TC6 & POST /api/event/create - Return 400 when missing required fields & 400 error response & Validation error returned & \cellcolor{green!30}Pass \\
\hline
TC7 & POST /api/event/create - Handle creation errors gracefully & 500 error response & Error caught and returned & \cellcolor{green!30}Pass \\
\hline
TC8 & PUT /api/events/:id - Update existing event & 200 status with updated data & Event fields updated correctly & \cellcolor{green!30}Pass \\
\hline
TC9 & PUT /api/events/:id - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
TC10 & PUT /api/events/:id - Convert date strings to Date objects & Date strings converted to Date objects in update & Dates properly formatted & \cellcolor{green!30}Pass \\
\hline
TC11 & GET /api/events/:id/registration - Return registration status for user & Registration status returned & User registration found & \cellcolor{green!30}Pass \\
\hline
TC12 & GET /api/events/:id/registration - Return false when user not registered & isRegistered field false & Correctly indicates no registration & \cellcolor{green!30}Pass \\
\hline
TC13 & GET /api/events/:id/registration - Return 400 when userEmail missing & 400 error response & Parameter validation error returned & \cellcolor{green!30}Pass \\
\hline
TC14 & GET /api/events/:id/registrationlist - Return list of registered users & Array of registrations returned & Registered users listed & \cellcolor{green!30}Pass \\
\hline
TC15 & GET /api/events/:id/registrationlist - Handle empty registration list & Empty array returned & Successfully handles empty list & \cellcolor{green!30}Pass \\
\hline
TC16 & GET /api/events/:id/registration-form - Return event registration form & Registration form questions returned & Form questions retrieved & \cellcolor{green!30}Pass \\
\hline
TC17 & GET /api/events/:id/registration-form - Return empty questions when form null & Empty questions array returned & Handles null form gracefully & \cellcolor{green!30}Pass \\
\hline
TC18 & GET /api/events/:id/registration-form - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
TC19 & GET /api/events/:id/registration-form - Transform questions to correct format & Questions properly formatted with required fields & Question format transformation correct & \cellcolor{green!30}Pass \\
\hline
TC20 & PUT /api/events/:id/registration-form - Update registration form & 200 status with updated form & Registration form updated successfully & \cellcolor{green!30}Pass \\
\hline
TC21 & PUT /api/events/:id/registration-form - Return 400 for invalid form & 400 error response & Form validation error returned & \cellcolor{green!30}Pass \\
\hline
TC22 & PUT /api/events/:id/registration-form - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
TC23 & PATCH /api/events/:id/check-in - Check in registered user & 200 status with attended status & User checked in successfully & \cellcolor{green!30}Pass \\
\hline
TC24 & PATCH /api/events/:id/check-in - Return 404 when user not found or already checked in & 404 error response & User status error returned & \cellcolor{green!30}Pass \\
\hline
TC25 & PATCH /api/events/:id/check-in - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
TC26 & GET /api/events/:id/qr-registration - Check QR code registration & Registration checked and returned & QR code validation successful & \cellcolor{green!30}Pass \\
\hline
TC27 & GET /api/events/:id/qr-registration - Return false when QR not found & isRegistered false & Correctly indicates no registration & \cellcolor{green!30}Pass \\
\hline
TC28 & GET /api/events/:id/qr-registration - Return 400 when registrationHash missing & 400 error response & Parameter validation error returned & \cellcolor{green!30}Pass \\
\hline
TC29 & GET /api/events/:id/qr-registration - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
TC30 & PATCH /api/events/:id/qr-check-in - Check in user via QR code & 200 status with check-in data & User QR check-in successful & \cellcolor{green!30}Pass \\
\hline
TC31 & PATCH /api/events/:id/qr-check-in - Return 400 when registrationHash missing & 400 error response & Parameter validation error returned & \cellcolor{green!30}Pass \\
\hline
TC32 & PATCH /api/events/:id/qr-check-in - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Events API Unit Tests}}

\subsubsection{Admin Server Testing - Forms API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{5cm}|>{\raggedright\arraybackslash}p{3.25cm}|>{\raggedright\arraybackslash}p{3.25cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC33 & GET /api/forms - Return all standard forms & Array of forms returned & Forms successfully retrieved & \cellcolor{green!30}Pass \\
\hline
TC34 & GET /api/forms/all - Return all forms including sub-forms & Complete forms array returned & All forms retrieved & \cellcolor{green!30}Pass \\
\hline
TC35 & GET /api/mod-forms - Return all modular forms & Modular forms array returned & Modular forms retrieved & \cellcolor{green!30}Pass \\
\hline
TC36 & GET /api/forms/:id - Return single form by ID & Form object with matching ID returned & Correct form retrieved & \cellcolor{green!30}Pass \\
\hline
TC37 & GET /api/forms/:id - Return 404 when form not found & 404 error response & Form not found error returned & \cellcolor{green!30}Pass \\
\hline
TC38 & POST /api/forms - Create new standard form & 201 status with created form data & Form created successfully & \cellcolor{green!30}Pass \\
\hline
TC39 & POST /api/forms - Return 400 when form name missing & 400 error response & Validation error returned & \cellcolor{green!30}Pass \\
\hline
TC40 & PUT /api/forms/:id - Update existing form & 200 status with updated form data & Form updated successfully & \cellcolor{green!30}Pass \\
\hline
TC41 & PUT /api/forms/:id - Return 404 when form not found & 404 error response & Form not found error returned & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Forms API Unit Tests}}

\subsubsection{Admin Server Testing - Form Builder API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC42 & POST /api/forms/:id/questions - Create new form question & 201 status with created question data & Question created successfully & \cellcolor{green!30}Pass \\
\hline
TC43 & POST /api/forms/:id/questions - Return 400 when questionType missing & 400 error response & Question validation error returned & \cellcolor{green!30}Pass \\
\hline
TC44 & GET /api/forms/:id/questions - Return all questions for form & Array of questions returned & Form questions retrieved & \cellcolor{green!30}Pass \\
\hline
TC45 & GET /api/forms/:id/questions - Return 404 when form not found & 404 error response & Form not found error returned & \cellcolor{green!30}Pass \\
\hline
TC46 & PUT /api/forms/:formId/questions/:questionId - Update form question & 200 status with updated question & Question updated successfully & \cellcolor{green!30}Pass \\
\hline
TC47 & DELETE /api/forms/:formId/questions/:questionId - Delete form question & 200 status with success message & Question deleted successfully & \cellcolor{green!30}Pass \\
\hline
TC48 & DELETE /api/forms/:formId/questions/:questionId - Return 404 when question not found & 404 error response & Question not found error returned & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Form Builder API Unit Tests}}

\subsubsection{Admin Server Testing - Images API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{5cm}|>{\raggedright\arraybackslash}p{3.25cm}|>{\raggedright\arraybackslash}p{3.25cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC49 & GET /api/images/:component - Return all images for component & Array of images returned & Images retrieved successfully & \cellcolor{green!30}Pass \\
\hline
TC50 & GET /api/images/:component - Handle empty result gracefully & Empty array returned & Successfully handles empty list & \cellcolor{green!30}Pass \\
\hline
TC51 & GET /api/images/:id/view - Return image file data & Image file returned with correct MIME type & Image data retrieved & \cellcolor{green!30}Pass \\
\hline
TC52 & GET /api/images/:id/view - Return 404 when image not found & 404 error response & Image not found error returned & \cellcolor{green!30}Pass \\
\hline
TC53 & DELETE /api/images/:id - Delete image & 200 status with success message & Image deleted successfully & \cellcolor{green!30}Pass \\
\hline
TC54 & DELETE /api/images/:id - Return 404 when image not found & 404 error response & Image not found error returned & \cellcolor{green!30}Pass \\
\hline
TC55 & GET /api/images/:component/:index - Return image by component and index & Image object returned & Correct image retrieved & \cellcolor{green!30}Pass \\
\hline
TC56 & GET /api/images/:component/:index - Return 404 when image not found & 404 error response & Image not found error returned & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Images API Unit Tests}}

\subsubsection{User Server Testing - Authentication API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC57 & POST /api/auth/register - Register new user with valid credentials & 201 status with user data & User successfully registered & \cellcolor{green!30}Pass \\
\hline
TC58 & POST /api/auth/register - Return 400 when email or password missing & 400 error response & Validation error returned & \cellcolor{green!30}Pass \\
\hline
TC59 & POST /api/auth/register - Return 400 for password less than 8 characters & 400 error response & Password length validation error & \cellcolor{green!30}Pass \\
\hline
TC60 & POST /api/auth/login - Return 401 with invalid credentials & 401 error response & Authentication error returned & \cellcolor{green!30}Pass \\
\hline
TC61 & POST /api/auth/logout - Clear authentication token & 200 status with success message & Token cleared successfully & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Authentication API Unit Tests}}

\subsubsection{User Server Testing - Events API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC62 & GET /api/events - Return all available events & Events array returned & All events retrieved & \cellcolor{green!30}Pass \\
\hline
TC63 & GET /api/events/:id - Return single event by ID & Event object with matching ID & Event successfully retrieved & \cellcolor{green!30}Pass \\
\hline
TC64 & GET /api/events/:id - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
TC65 & POST /api/events/:id/register - Register user for event & 201 status with registration data & User event registration created & \cellcolor{green!30}Pass \\
\hline
TC66 & POST /api/events/:id/register - Return 400 when userEmail missing & 400 error response & Parameter validation error returned & \cellcolor{green!30}Pass \\
\hline
TC67 & POST /api/events/:id/register - Return 404 when event not found & 404 error response & Event not found error returned & \cellcolor{green!30}Pass \\
\hline
TC68 & POST /api/events/:id/register - Register with event registration details & 201 status with registration & Registration with details created & \cellcolor{green!30}Pass \\
\hline
TC69 & POST /api/events/:id/register - Return 400 for duplicate registrations & 400 error response & Duplicate registration error & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Events API Unit Tests (User Server)}}

\subsubsection{User Server Testing - Forms API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC70 & GET /api/forms - Return all public forms & Forms array returned & All public forms retrieved & \cellcolor{green!30}Pass \\
\hline
TC71 & GET /api/forms/available/:uid - Return unfilled forms for user & Available forms array & User available forms retrieved & \cellcolor{green!30}Pass \\
\hline
TC72 & GET /api/forms/completed/:uid - Return completed forms for user & Completed forms array & User completed forms retrieved & \cellcolor{green!30}Pass \\
\hline
TC73 & GET /api/forms/:fid - Return single form by ID & Form object with matching ID & Form successfully retrieved & \cellcolor{green!30}Pass \\
\hline
TC74 & GET /api/forms/:fid - Return 404 when form not found & 404 error response & Form not found error returned & \cellcolor{green!30}Pass \\
\hline
TC75 & GET /api/mod-forms/:fid - Return single modular form by ID & Modular form object & Modular form retrieved & \cellcolor{green!30}Pass \\
\hline
TC76 & POST /api/forms/:fid/answers/:uid - Post form answer for question & 201 status with answer data & Form answer created successfully & \cellcolor{green!30}Pass \\
\hline
TC77 & PATCH /api/forms/:fid/submit/:uid - Submit completed form & 200 status with submission data & Form submission created & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Forms API Unit Tests (User Server)}}

\subsubsection{User Server Testing - Images API}

\noindent
\begin{longtable}{|>{\raggedright\arraybackslash}p{1cm}|>{\raggedright\arraybackslash}p{4.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{3.5cm}|>{\raggedright\arraybackslash}p{1.5cm}|}
\hline
\textbf{ID} & \textbf{Action} & \textbf{Expected Result} & \textbf{Actual Result} & \textbf{Result} \\\hline
\endhead
\hline
TC78 & GET /api/images/event/:eventId - Return event image by event ID & Image file with correct MIME type & Image data retrieved & \cellcolor{green!30}Pass \\
\hline
TC79 & GET /api/images/event/:eventId - Return 400 for invalid event ID & 400 error response & Invalid ID error returned & \cellcolor{green!30}Pass \\
\hline
TC80 & GET /api/public/images/:component - Return all images for component & Array of images returned & Component images retrieved & \cellcolor{green!30}Pass \\
\hline
TC81 & GET /api/public/images/:id/view - View specific image file by ID & Image file returned with MIME type & Image successfully viewed & \cellcolor{green!30}Pass \\
\hline
TC82 & GET /api/public/images/:id/view - Return image with correct headers & Image with caching headers & Image returned with cache control & \cellcolor{green!30}Pass \\
\hline
\end{longtable}

\vspace{0.5cm}

{\small \textit{Table: Images API Unit Tests (User Server)}}

\section{Changes Due to Testing}

\wss{This section should highlight how feedback from the users and from 
the supervisor (when one exists) shaped the final product.  In particular 
the feedback from the Rev 0 demo to the supervisor (or to potential users) 
should be highlighted.}

\section{Automated Testing}
		
\section{Trace to Requirements}
		
\section{Trace to Modules}		

\section{Code Coverage Metrics}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item Which parts of this document stemmed from speaking to your client(s) or
  a proxy (e.g. your peers)? Which ones were not, and why?
  \item In what ways was the Verification and Validation (VnV) Plan different
  from the activities that were actually conducted for VnV?  If there were
  differences, what changes required the modification in the plan?  Why did
  these changes occur?  Would you be able to anticipate these changes in future
  projects?  If there weren't any differences, how was your team able to clearly
  predict a feasible amount of effort and the right tasks needed to build the
  evidence that demonstrates the required quality?  (It is expected that most
  teams will have had to deviate from their original VnV Plan.)
\end{enumerate}

\end{document}